### 2019-05-28 thesis_proposal_LaTeX/Chapters/2_ProblmemDefinitionAndMotivation.tex
candidate polys

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis. The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}. In the past years, photon polymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist. \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures \cite{Hribar2014}.

On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner. Cardenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis. Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires. As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production. Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.

>>>>

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis, as it is generally believed that most polymers do not form significant amounts of graphitic carbon when carbonized.
%The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
In the past years, photopolymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist. \cite{Boer2014} Photopolymerization techniques deliver patterning resolutions with nano-scale tolerances through two-photon lithography for the production of highly detailed structures \cite{Hribar2014}.

On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner. Cardenas \cite{Cardenas2017} showed that electrospinning can be implemented with ease for carbon nano-wire synthesis. Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires. As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production. Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.

### 2019-05-28 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
candidate polys

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length). The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work. PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but no benefit is obtained from it after pyrolysis.

@@

\begin{itemize}
	\item{
	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
	}
	\item{
	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
	}
	\item{
	What rheological properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
	}
	\item{
	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
	}
	\item{
	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
	}
	\item{
	What PEO-similar materials can be used to allow the electrospinning technique and favor the carbon nano-wire properties after pyrolysis? 
	}
\end{itemize}

>>>>

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the fabrication conductive of carbon nano-wires with specified dimensions (diameter and length). The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work. PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but no benefit is obtained from it after pyrolysis.

@@

\begin{itemize}
	\item{
	Is there any evidence of conductive carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
	}
	\item{
	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
	}
	\item{
	What rheological properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
	}
	\item{
	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
	}
	\item{
	What are the optimal fabrication parameters for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
	}
	\item{
	What materials can be used to ease the electrospinning process and favor the carbon nano-wire properties after pyrolysis? 
	}
\end{itemize}

### 2019-05-28 thesis_proposal_LaTeX/Chapters/6_TheoreticalFramework.tex
min fix
candidate polys

\section{Photoresists}
The electronic industry requires a sustainable raw material supply for its development \cite{Sutikno2016}. Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}. The additive requires to be with low molecular weight as it is intended to act as a photosensitive material. Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}. Photoresists are classified into two categories. The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}. In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.

@@

In summary, a photoresist is an "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}

@@

\section{Rheometry}
Rheometry is the measuring technology used to determine rheological data. There are different measuring systems, instruments and analysis methods. Both, liquids and solid  can be investigated using rotational and oscillatory rheometers. Rotational tests are performed to characterize viscous behavior. In order to evaluate viscoelastic behavior, creep tests, relaxation tests and oscillatory tests are performed \cite{Flores2017}.

\subsection{Amplitude Sweep}
An amplitude sweep is a typical test used to characterize the behavior of a polymer
solution or polymer melt. In this basic test a constant angular frequency is applied along with an increasing or decreasing deformation or strain, see Figure \ref{fig:ampSweep} a). The obtained results are the storage and loss moduli, $G'$ and $G''$ respectively, along the values of percentage of strain applied. The amplitude is the maximum of the oscillatory motion. Normally at low frequencies the viscoelastic material presents a linear behavior, this is when the viscoelastic properties are independent of the strain or stress imposed due to the structure of the material stays undisturbed. Nevertheless, as the amplitude is increased at some at some point this linear trend changes suddenly. Once this critical amplitude value is reached the material becomes more elastic or viscous depending on the solution initial state, see Figure \ref{fig:ampSweep} b) \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/ampSweep.png}
\decoRule
\caption[Amplitude Sweep]{a) Imposed amplitude along time with constant frequency. b) Results for an amplitude sweep \cite{Flores2017}}
\label{fig:ampSweep}
\end{figure}

\subsection{Frequency Sweep}
A frequency sweep, is a common oscillatory test useful to understand the rheological behavior of fluids as it measures the viscoelastic properties. This measurement is considered a viscoelastic spectrum, in general, the shorter the timescale the more elastic the material behaves. These results are related to the molecular structure of the sample. Figure \ref{fig:freqSweep} shows a typical data for a polymer melt where different regions are observed. Frequency sweep measurements also allow the estimation of the molecular weight distribution characteristics such as entanglement density and process-ability \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/freqSweep.png}
\decoRule
\caption[Frequency Sweep]{Typical results for a frequency sweep. \cite{Flores2017}}
\label{fig:freqSweep}
\end{figure}

\subsection{Flow Curve}
The viscosity is measured as a function of the shear rate in a rotational rheometer with different geometries according to the sample. Normally three types of behaviours can be characterized in flow curve measurements: a) ideal viscous, b) shear thinning and c) shear thickening. Figure \ref{fig:flowCurve} shows three different materials and their response to an imposed shear rate \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/flowCurve.png}
\decoRule
\caption[Flow Curves]{a) Flow curve stress vs stress. b) Flow curve strain vs shear viscosity. Both figures for i Newtonian fluid, ii Shear thinning fluid, iii Shear thickening fluid. \cite{Flores2017}}
\label{fig:flowCurve}
\end{figure}

@@

To verify Flores' work \cite{Flores2017}, a series of rheological measurements have been executed. Since one purpose of the proposed dissertation is to replace

>>>>

\section{Photoresists}
The electronic industry requires a sustainable raw material supply for its development \cite{Sutikno2016}. Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}. The additive requires to be with low molecular weight as it is intended to act as a photosensitive material. Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}. Photoresists are classified into two categories. The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}, see Figure \ref{fig:PosNegResist}. In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.

\begin{figure}[th]
\centering
\includegraphics[width=0.55\textwidth]{./Figures/PosNegResist.jpg}
\decoRule
\caption[Positive and negative resist exposure and development]{Positive and negative resist exposure and development \cite{Hoggan2002}}
\label{fig:PosNegResist}
\end{figure}

@@

In summary, a photoresist is a "resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}

@@

@@

\subsection{Materials and Sample Preparation}

To verify Flores' work \cite{Flores2017}, a series of rheological measurements have been executed. For that purpose, the solutions in Flores work were recreated as follows: The polymer system in the study is SU-8 2002 (SU-8, an epoxy-based negative photoresist) dissolved in cyclopentanone with poly(ethylene oxide (PEO) to alter the viscoelastic properties of the polymer solution, and tetrabutylammonium tetrafluoroborate (TBATFB) to enhance the conductivity. Flores's results are listed in Section \ref{sec:FloresWrk}

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/PEset1.png}
\decoRule
\caption[Set 1 of the Recreation of Flores' "Serie B`` Samples]{Set 1 of the Recreation of Flores' Serie B`` Samples}
\label{fig:PEset1}
\end{figure}

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/PEset2.png}
\decoRule
\caption[Set 2 of the Recreation of Flores' "Serie B`` Samples]{Set 2 of the Recreation of Flores' "Serie B`` Samples}
\label{fig:PEset2}
\end{figure}

The samples were prepared as follows, the suitable amounts of PEO and TBATFB were added to 5 $mL$ of SU-8 in a 20 $mL$ vial and stirred at 160 $r p m$ during 1 hour at 75 $^\circ C$. The proportions are represented in $w t \%$. The samples with higher PEO concentration required to be stirred for more time to get rid of all PEO bundles. In order to avert cross-linking of SU-8 threads, during the stirring, the samples were isolated from light. a 5 $mL$ syringe of was used to extract the solution from the vial. The recreated sample concentrations are depicted in Serie B within Table \ref{tbl:FloresSamples}.

During the preliminary experiments, unlike to Flores' work, only the flow curve characterization was executed for two sample sets, as evidenced in Figures \ref{fig:PEset1} and \ref{fig:PEset2}. The two sets were characterized by the generation of flow curves with a "TA Instruments`` Discovery Hybrid Rheometer (DHR) at Tecnológico de Monterrey Campus Estado de México. The instrument's configuration was as follows:

\begin{itemize}
	\item Geometry: 60 $mm$, cone plate, peltier plate steel
	\item Temperature: 20 $^\circ C$
	\item Soak Time: 30.0 $s$
	\item Shear rate: 0.004 to 0.03 $Hz$
	\item Points per decade: 25
\end{itemize}

\subsection{Results}

As stated by Flores \cite{Flores2017}, it is expected an increase in viscosity with the increase of PEO concentration. However, the rheological results of set 1 (Figure \ref{fig:PEset1results}) do not follow the expectations, as the 0.75 $w t \%$ PEO concentration is less viscous than the 0.50 concentration; and the 0.25 $w t \%$ PEO concentration is more viscous than the 0.75 concentration. On the other hand, results are not consistent with Flores' results as the viscosity values are as high as 200 $Pa.s$ as depicted in Figure \ref{fig:PEset1results}. The supposed values are to be around 0.0 and 10.0 $Pa.s$.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/PEset1results.png}
\decoRule
\caption[Set 1 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples]{Set 1 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples}
\label{fig:PEset1results}
\end{figure}

As shown in Figure \ref{fig:PEset1}, inconsistencies between Flores' work and the current flow curves have been for not stirring the samples until all the PEO lumps get completely dissolved in cyclopentanone. The lack of stirring, generated unknown PEO concentrations within each sample, hence the inconsistent results.

For set 2, the rheological flow curve characterization was performed in the same way as in set 1, however, each sample was stirred for approximately 20 minutes before the characterization process. See Figure \ref{fig:PEset2}. Set 2 results, as depicted in Figure \ref{fig:PEset2results}, are consistent with the expectations. However, unlike Flores' results, the replicated flow curves have a less stable/constant value as they present a more pronounced shear thinning behaviour. The difference in the shear thinning behaviours shown in Figure \ref{fig:PEset2results} (preliminary experiment, set 2 results) and Figure \ref{fig:SerieBflowCurve} (Flores' results \cite{Flores2017}) may be caused by: 1) the use of different measurement instruments during the characterization process; and 2) the cyclopentanone solvent evaporation.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/PEset2results.png}
\decoRule
\caption[Set 2 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples]{Set 2 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples}
\label{fig:PEset2results}
\end{figure}

%Does the viscosity of cyclopentanone coincide with the reported value in the literature? Can you make a table comparing your zero shear viscosity values against Flores'?

\begin{table}[th]
\caption{Method 1 and Method 2 conditions and parameters \cite{Cardenas2017}}
\begin{center}
\begin{tabular}{ >{\raggedright\arraybackslash}p{0.08\textwidth} >{\raggedright\arraybackslash}p{0.27\textwidth} >{\raggedright\arraybackslash}p{0.27\textwidth} >{\raggedright\arraybackslash}p{0.27\textwidth} } 
\hline
Sample & PEO concentration [$w t \%$] & Preliminary zero shear viscosity measurements [$Pa.s$] & Flores' zero shear viscosity measurements [$Pa.s$] \\
\hline
1 & 0.00 & 0.31 & 0.03 \\
2 & 0.25 & 0.88 & 0.3 \\
3 & 0.50 & 1.42 & 0.4 \\
4 & 0.75 & 7.28 & 2 \\
5 & 1.00 & 9.25 & 3 \\
\hline
\label{tbl:FloresCompare}
\end{tabular}
\end{center}
\end{table}

Table \ref{tbl:FloresCompare} compares the current zero shear viscosity measurements and Flores' measurements. The comparison shows that both measurements have the same behaviour with similar proportions, as the zero shear viscosity increases with the increase of PEO concentration. However, the results show that the current measured values are approximately three times larger that Flores' measurements.

### 2019-05-28 thesis_proposal_LaTeX/Chapters/7_Methodology.tex
candidate polys

\section{Work package 1 : Preliminary Literature Review}
The first step to the thesis development is the study of preliminary literature and related work. The purpose of this work package is the familiarization of the existing techniques such as: far and near field electrospinning, lithography, pyrolysis, carbonization and photopolymerization. On the other hand, some research is to be done in order to recognize if there are any efforts in the design of electrospun-able, photopolymerizable and pyrolysable polymer solutions.

@@

\section{Work package 2 : Evaluation of Fabrication Parameters}
As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact on the quality of the carbon nano-wires. For that reason two tasks are to be executed:

@@

\section{Work package 3 : Polymer Solution Design}
Once the process parameters and rheological properties that affect the fabrication of carbon nano-wires are identified, the design process shall take place. This work package is to study polymer solutions that can be electrospun by NFES, photopolymerized and pyrolyzed. The polymer solution design will comprise of two steps:

@@

\section{Work package 4 : Fabrication of Carbon Nano-wires}
From the rheological analyses, determine and control the polymer solution properties and fabricate carbon nano-wires.

@@

\section{Work package 5 : Data Collection and Analysis of Results}
The data collection work package comprehends the study of the created carbon nano-wires using the new design polymer solution. The purpose is characterize the carbon nano-wires and compare them to the carbon nano-structures produced by existing techniques.

\section{Work package 6 : Documentation}
Finally the documentation refers to the Thesis writing tasks. This task is intended to carry out through the entire thesis development process, as every work package above is to be referenced within the thesis document.

>>>>

\section{Preliminary Literature Review}
The first step to the thesis development is the study of preliminary literature and related work. The purpose of this work package is the familiarization of the existing techniques such as: far and near field electrospinning, lithography, pyrolysis, carbonization and photopolymerization. On the other hand, some research is to be done in order to recognize if there are any efforts in the design of electrospun-able, photopolymerizable and pyrolysable polymer solutions.

@@

\section{Evaluation of Fabrication Parameters}
As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact on the quality of the carbon nano-wires. For that reason two tasks are to be executed:

@@

\section{Polymer Solution Design}
Once the process parameters and rheological properties that affect the fabrication of carbon nano-wires are identified, the design process shall take place. This work package is to study polymer solutions that can be electrospun by NFES, photopolymerized and pyrolyzed. The polymer solution design will comprise of two steps:

@@

\section{Fabrication of Carbon Nano-wires}
From the rheological analyses, determine and control the polymer solution properties and fabricate carbon nano-wires.

@@

\section{Data Collection and Analysis of Results}
The data collection work package comprehends the study of the created carbon nano-wires using the new design polymer solution. The purpose is characterize the carbon nano-wires and compare them to the carbon nano-structures produced by existing techniques.

\section{Documentation}
Finally the documentation refers to the Thesis writing tasks. This task is intended to carry out through the entire thesis development process, as every work package above is to be referenced within the thesis document.
